Coherent optical creation of a single molecule

### 2020-11-25 paper.tex
Update captions and include fitting parameters

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-theory.pdf}
  \caption{Optical creation of single molecule from single atoms in tweezer.
    (a) Schematic of the optical transition from an atom pair to a weakly bound molecule.
    The initial state is the relative motional ground state between the two atoms
    and the final state is the first molecular bound state.
    The transition is driven by a pair of laser frequencies matching the binding energy
    of the molecule.
    The lasers are detuned from an excited molecular state in the $\mathrm{c^3\Sigma}$ potential
    by $\Delta$ in order to suppress scattering during the transfer.
    (b) Comparison between using a weakly bound and a deeply bound excited state
    as intermediate state for the Raman transition.
    The deeply bound excited state (upper half $v'=0$)
    has a smaller Raman Rabi frequency ($\Omega_{R}$)
    compared to the weakly bound excited state (lower half $v'=63$) at a given detuning.
    However, the scattering rate ($\Gamma_{s}$) is also much lower,
    which results in a larger ratio of Raman Rabi frequency to scattering rate.
    (c) Enhancement of the short-range wavefunction.
    The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
    comparable to the axial trapping frequency.
    This causes a significant change in the relative wavefunction, especially at short
    internuclear distance ($R$).
    Compared to other spin states with weaker interaction,
    the wavefunction at short distance ($R<100\ \text{\AA}$, left of the dotted line)
    is significantly enhanced.
    \label{f-theory}
  }
\end{figure*}

@@

\begin{figure}[t!]
  \includegraphics[width=0.48\textwidth]{imgs/fig-lifetime.pdf}
  \caption{
    (a) Direct measurement of molecule lifetime in a trap of depth $3.75~\mathrm{mW}$.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
    measured from the Raman transition data.
    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
    in a trap of depth $3.75~\mathrm{mW}$ caused by off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    Inset: Atomic scattering rate scales as $P_\textrm{tweezer}^{2.58}$ on a log-log scale;
    this is consistent with a two-photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    \label{f-lifetime}}
\end{figure}

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    The detuning is calculated from the closest $v'=0$ PA frequency at $288703.6~\mathrm{GHz}$.
    (a) The light shift of the Raman resonance scales as $P$
    and follows $1/\Delta$ with an offset, where $ P$ is the power in the tweezer.
    The fit also includes a small term that is proportional to $P^2$
    which is caused by the effective magnetic field generated by the tweezer, which is perpendicular to the real magnetic field.
    (b) Raman Rabi frequency ($\Omega_R$) scales as $P^{1.29}$
    and follows $1/\Delta$ with an offset.
    (c) Tweezer power dependency of light shift (up) and Raman Rabi frequency (down)
    on a log-log plot showing the power-law scaling.
    \label{f-det}}
\end{figure*}

>>>>

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-theory.pdf}
  \caption{Optical creation of single molecule from single atoms in tweezer.
    (a) Schematic of the optical transition from an atom pair to a weakly bound molecule.
    The initial state is the relative motional ground state between the two atoms
    and the final state is the first molecular bound state.
    The transition is driven by a pair of laser frequencies matching the binding energy
    of the molecule.
    The lasers are detuned from an excited molecular state in the $\mathrm{c^3\Sigma}$ potential
    by $\Delta$ in order to suppress scattering during the transfer.
    (b) Comparison between using a weakly bound and a deeply bound excited state
    as intermediate state for the Raman transition.
    The deeply bound excited state (blue lines $v'=0$)
    has a smaller Raman Rabi frequency ($\Omega_{R}$)
    compared to the weakly bound excited state (orange lines $v'=40$) at a most detuning.
    However, the scattering rate ($\Gamma_{s}$) is also much lower,
    which results in a larger ratio of Raman Rabi frequency to scattering rate.
    (c) Enhancement of the short-range wavefunction.
    The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
    comparable to the axial trapping frequency.
    This causes a significant change in the relative wavefunction, especially at short
    internuclear distance ($R$).
    Compared to other spin states with weaker interaction,
    the wavefunction at short distance ($R<100\ \text{\AA}$, left of the dotted line)
    is significantly enhanced.
    \label{f-theory}
  }
\end{figure*}

@@

\begin{figure}[t!]
  \includegraphics[width=0.48\textwidth]{imgs/fig-lifetime.pdf}
  \caption{
    (a) Direct measurement of molecule lifetime in a trap of depth $3.75~\mathrm{mW}$.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
    measured from the Raman transition data.
    Inset: pulse sequence for the lifetime measurement.
    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
    in a trap of depth $3.75~\mathrm{mW}$ caused by off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    Inset: Atomic scattering rate scales as
    $P_\textrm{tweezer}^{2.58}\cdot\!2\pi\!\cdot29.3(17)~\mathrm{mHz/mW^{2.58}}$ on a log-log scale;
    this is consistent with a two-photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    \label{f-lifetime}}
\end{figure}

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    The detuning is calculated from the closest $v'=0$ PA frequency at $288703.6~\mathrm{GHz}$.
    (a) The light shift of the Raman resonance fitted to
    $(f_{R0}+a\cdot P+b\cdot P^2)+c\cdot P/\Delta$
    where $P$ is the power in the tweezer,
    $\Delta\equiv f_{\mathrm{PA}0} - f_{\mathrm{tweer}}$ is the detuning from
    the PA resonance frequency $f_{\mathrm{PA}0}$.
    The small $P^2$ term included in the fit is caused by the effective magnetic field
    generated by the tweezer, which is perpendicular to the real magnetic field.
    The fitting results are $f_{\mathrm{PA}0}=288711~\mathrm{GHz}$,
    $f_{R0}=770.20052(2)~\mathrm{MHz}$, $a=8.78(7)~\mathrm{kHz/mW}$,
    $b=-3.186(9)~\mathrm{kHz/mW^2}$
    and $c=16.43(2)~\mathrm{MHz\cdot GHz/mW}$.
    (b) Raman Rabi frequency ($\Omega_R$) fitted to $(a + b/\Delta)\cdot P^{1.29}$.
    The detuning is calculated using the PA frequency fitted in (a).
    The fitting results are $a=-2\pi\cdot\!0.41(2)~\mathrm{kHz/mW^{1.29}}$
    $b=4\pi^2\cdot\!167(2)~\mathrm{kHz\cdot\!GHz/mW^{1.29}}$.
    (c) Tweezer power dependency of light shift (top) and Raman Rabi frequency (bottom)
    on a log-log plot showing the power-law scaling.
    \label{f-det}}
\end{figure*}
